Difference-in-Differences with Spatial Spillovers

### 2021-10-27 latex/slides/Spillover_slides.tex
Removed too large file

\documentclass[aspectratio=169]{beamer}
% Metropolis Theme ------------------------------------------------------------------------------
\usetheme{metropolis} % Use metropolis theme

@@

\usepackage{adjustbox}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{dcolumn}

% Table Highlighting
\usepackage[beamer,customcolors]{hf-tikz}
\usetikzlibrary{calc}
\usetikzlibrary{fit,shapes.misc}

% To set the hypothesis highlighting boxes red.
\tikzset{hl/.style={
    set fill color=red!80!black!40,
    set border color=red!80!black,
  },
}
\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-a) at (0,1.5ex) {};%
}
\newcommand\markbottomright[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-b) at (0,0) {};%
    \tikz[red, ultra thick, overlay, remember picture, inner sep=4pt]
        \node[draw, rectangle, fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
}

@@

    \vspace{5mm}
    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries (states, counties, etc.). Example:

    \begin{itemize}
        \item A large employer opening/closing in a treated county have positive employment effects on \textbf{control counties}

        \item Having nearby counties with factories raises wages and reduces effect of \textbf{treated counties}
    \end{itemize}
\end{frame}

\begin{frame}{This Paper}
    In this paper, I

    \begin{itemize}
        \item Present a potential outcomes framework to formalize spillover effects and evaluate ad-hoc adjustments done in the literature

@@

    \onslide<1->{
        The canonical difference-in-differences estimate is: 
        \only<1>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Counterfactual Trend}}
            \]
        }
        \only<2>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{purple} Spillover on Control}}}
            \]
        }
        \only<3>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\substack{\text{Counterfactual Trend} \ + \ \tau \\[2mm] \ + \ \text{\color{red} Spillover on Treated}}} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{purple} Spillover on Control}}}
            \]
        }
    }

    Two problems in presence of spillover effects:

    \begin{itemize}
        \onslide<2->{
            \item {\bf \color{purple} Spillover onto Control Units:}

@@

        \onslide<3->{
            \vspace{2.5mm}
            \item {\bf \color{red} Spillover onto other Treated Units:}

            Treated units are also affected by nearby units and therefore combines ``direct'' effects with spillover effects
        }
    \end{itemize}

@@

\begin{frame}{Remove Bias}
    \only<1>{
        \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
    }
    \only<2>{
        \[ 
            y_{it} = \mu_t + \mu_i + \tau D_{it} + \text{Within}_{it} * D_{it} + \text{Within}_{it} * (1-D_{it}) + \varepsilon_{it}
        \]
    }

    \only<1>{ 
        \[ 
            \mathbb{E}\{\hat{\tau}\} = \tau + \text{\color{purple} Spillover on Control} + \text{\color{red}Spillover on Treated}
        \]
    }
    \only<2>{
        \[ 
            \mathbb{E}\{\hat{\tau}\} = \tau,
        \]
        so long as $\text{Within}_{it}$ contains all the units with spillovers.
    }
\end{frame}

@@

            \vspace{2.5mm}
            \item Discuss how framework can reconcile conflicting findings on effect of federal Empowerment Zones \begin{citecolor}\citep{Busso_Gregory_Kline_2013,Neumark_Kolko_2010}\end{citecolor}
        \end{itemize}
    \end{itemize} 
\end{frame}

@@

    \begin{itemize}
        \item $Y_{it}(D_i, \textcolor{blue}{h(\vec{D}, i)})$ is the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.

@@

        \pause
        \item The function $\textcolor{blue}{h(\vec{D}, i)}$ maps the entire treatment vector into an `exposure mapping' which can be a scalar or a vector.

        \pause
        \item No exposure is when $\textcolor{blue}{h(\vec{D}, i)} = \vec{0}$.
    \end{itemize}
\end{frame}

@@

        $\textcolor{blue}{h(\vec{D}, i)} = max_j \ 1(d(i, j) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.

@@

@@

        $\textcolor{blue}{h(\vec{D}, i)} = max_j \ 1(d(i, j) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.

@@

        $\textcolor{blue}{h(\vec{D}, i)} = \sum_{j = 1}^k 1(d(i, j) \leq x)$.

        \begin{itemize}
            \item e.g. large factories opening

@@

\begin{frame}{Estimand of Interest}
    Estimand of Interest: 
    \[ 
        \textcolor{green}{\tau_{\text{direct}}} \equiv \textcolor{green}{\mathbb{E}\left[ Y_{i,1}(1, 0) - Y_{i,1}(0, 0) \mid D_i = 1\right]}
    \]

    \pause
    \vspace{2.5mm}
    Spillover Effects:

    \[
        \textcolor{red}{\tau_{\text{spillover, treated}}} \equiv \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]}
    \]

    \[ 
        \textcolor{purple}{\tau_{\text{spillover, control}}} = \textcolor{purple}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]}
    \]
\end{frame}

@@

    \textbf{Assumption:} \textit{Parallel Counterfactual Trends}
    \begin{align*}
        &\mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{blue}{\vec{0}}) - Y_{i,0}(0, \textcolor{blue}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 1 \big] \\
        = \ &\mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{blue}{\vec{0}}) - Y_{i,0}(0, \textcolor{blue}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 0 \big],
    \end{align*}

@@

    Changes in outcomes does not depend on treatment status

@@

    \begin{align*}
        \mathbb{E}\left[\hat{\tau}\right] &= \underbrace{\mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Difference-in-Differences}} \\[3mm]
        \pause&= 
        \textcolor{green}{\mathbb{E} \left[ Y_{i1}(1, 0) - Y_{i1}(0, 0) \mid D_i = 1 \right]} \\
        &\quad + \quad 
        \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]} \\ 
        &\quad - \quad  
        \textcolor{purple}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\[3mm]
        &= \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
    \end{align*}

@@

\begin{frame}{Removing Bias}
    \textbf{Assumption:} \textit{Spillovers are Local}

@@

        (i) For all units $i$,
        \[ 
            \min_{j: \ D_j = 1} d(i,j) > \bar{d} \implies h(\vec{D}, i) = \vec{0}. 
        \]

        (ii) There are treated and control units such that $\min_{j: \ D_j = 1} d(i,j) > \bar{d}$.
\end{frame}

\begin{frame}{Removing Bias}
    With assumption that spillovers are local, define $S_i$ to be an indicator that contains all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).

    Then $\hat{\tau}$ will be a consistent estimate for $\tau$ in this specification: 
    \[ 
        y_{it} = \mu_t + \mu_i + \tau D_{it} + \text{Within}_{it} * D_{it} + \text{Within}_{it} * (1-D_{it}) + \varepsilon_{it}
    \]

@@

% ------------------------------------------------------------------------------
\section{Estimation with Spillovers}
% ------------------------------------------------------------------------------

\begin{frame}{Common Solution: Removing ``contaminated'' controls}
    A common solution to the problem of spillover is to restimate on a subsample with neighboring control units removed.

@@

\begin{frame}{Solution: Parametrize potential outcomes}
    Another option is to directly control for spillovers by parametrizing the exposure mapping.

    The corret exposure mapping is not observable to a researcher which raises the question:

    Are there specifications that work well even if the spillovers are misspecified?
\end{frame}

\begin{frame}{Robustness to Misspecification}
    Generate data using the same data-generating process as before but with different spillover functions:

@@

    \begin{itemize}
        \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly.
    \end{itemize}

@@

        \item \textit{Decay}: 
        \begin{itemize}
            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
        \end{itemize}

@@

        \item \textit{Decay}: 
        \begin{itemize}
            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
        \end{itemize}

        \item \textit{Rings}: 
        \begin{itemize}
            \item Set of concentric rings. For each ring, indicator for nearest treated unit being within that distance bin
        \end{itemize}

@@

        \begin{adjustbox}{width = 1.1\textwidth, center}
            \begin{threeparttable}
                \begin{tabular}{@{} l rrrrrr @{}}
                    % Head
                    \toprule
                    & \multicolumn{6}{c}{Data-Generating Process} \\
                    \cmidrule{2-7}

@@

    \onslide<3->{
        \textbf{Indicator (or set of indicators) that captures all affected unit removes all bias}
    }
\end{frame}

@@

    However, the two other spillover effects are of interest as well:
    \begin{itemize}
        \item $\textcolor{purple}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?

@@

@@

    Research Question: What are the local effects of TVA on manufacturing and agricultural economies? Do these effects come at the cost of other counties?
\end{frame}

@@

    \begin{itemize}
        \item $\text{Ring}(d)$ is a set of indicators for being in the following distance bins (in miles) from the Tennessee Valley Authority: 
        \[ d \in \left\{ (0, 50], (50, 100], (100, 150] \right\} \]
    \end{itemize}
\end{frame}

@@

    \begin{adjustbox}{width = 1\textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} lc@{\extracolsep{20pt}}c@{\extracolsep{4pt}}ccc @{}}
                % Head
                \toprule

                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
                \cmidrule{2-2} \cmidrule{3-6} 
                & & & TVA between & TVA between & TVA between \\ 
                \textit{Dependent Var.} & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. \\

@@

                Agricultural employment     & $-0.0514^{***}$& $-0.0678^{***}$& $-0.0310^{**}$ &    $-0.0112$   & $-0.0252^{***}$\\
                &   $(0.0087)$   &   $(0.0102)$   &   $(0.0123)$   &   $(0.0094)$   &   $(0.0084)$

                \onslide<2->{
                    \\
                    Manufacturing employment    & $0.0560^{***}$ &  $0.0461^{**}$ &    $-0.0104$   &    $-0.0128$   &  $-0.0248^{*}$ \\
                    &   $(0.0187)$   &   $(0.0210)$   &   $(0.0205)$   &   $(0.0257)$   &   $(0.0147)$
                }

@@

    \begin{itemize}
        \pause
        \item \citet{Busso_Gregory_Kline_2013} compare census tracts in Empowerment Zones to census tracts that qualified and were rejected from the program. They find significant large reduction of poverty.

@@

>>>>

\documentclass[aspectratio=169]{beamer}

@@

@@

    \vspace{5mm}
    \textbf{Spillover effects} occur when the effect of treatment extends over the treatment boundaries (states, counties, etc.). Example: Amazon Shipping Center

    \begin{itemize}
        \item A shipping center opening in county \textit{c} has positive employment effects on \textbf{nearby control counties}

        \item Having nearby counties with shipping centers raises employment and therefore reduces the effect of \textbf{treated counties} through general equilibrium effects
    \end{itemize}
\end{frame}

\begin{frame}{This Paper}
    In this paper, I...

    \begin{itemize}
        \item Present a potential outcomes framework to formalize spillover effects and evaluate ad-hoc adjustments commonly found in the literature

@@

    \onslide<1->{
        The canonical difference-in-differences estimate is: 
        \only<1>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Counterfactual Trend}}
            \]
        }
        \only<2>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{coral} Spillover on Control}}}
            \]
        }
        \only<3>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\substack{\text{Counterfactual Trend} \ + \ \tau \\[2mm] \ + \ \text{\color{kelly} Spillover on Treated}}} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{coral} Spillover on Control}}}
            \]
        }
    }

    Two problems occur in the presence of spillover effects:

    \begin{itemize}
        \onslide<2->{
            \item {\bf \color{coral} Spillover onto Control Units:}

@@

        \onslide<3->{
            \vspace{2.5mm}
            \item {\bf \color{kelly} Spillover onto other Treated Units:}

            Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
        }
    \end{itemize}

@@

\begin{frame}{Remove Bias}
    \only<1>{
        \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
    }
    \only<2>{
        \[ 
            y_{it} = \mu_t + \mu_i + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}} +  + \varepsilon_{it}
        \]
    }

    \only<1>{ 
        \[ 
            \mathbb{E}[\hat{\tau}] = \tau + \text{\color{coral} Spillover on Control} + \text{\color{kelly}Spillover on Treated}
        \]
    }
    \only<2>{
        \[ 
            \mathbb{E}[\hat{\tau}] = \tau,
        \]
        so long as $\text{Within}_{it}$ contains all the units with spillovers.
    }
\end{frame}

\begin{frame}
    \begin{figure}[tb!]
        \caption{Single Ring - Removes spillover effects}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics{../../figures/figure-within_example.pdf}
            }
        \end{center}
    \end{figure}
\end{frame}

\begin{frame}
    \begin{figure}[tb!]
        \caption{Multiple Rings - Improves estimation of spillover effects}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics{../../figures/figure-rings_example.pdf}
                } 
            \end{center}
    \end{figure}
\end{frame}

% \begin{frame}
%     \begin{figure}[tb!]
%         \caption{Community Health Centers}
%         \begin{center}
%             \resizebox{0.9\textwidth}{!}{
%                 \includegraphics{../../figures/figure-chc-es_combined_slides.pdf}
%                 } 
%             \end{center}
%     \end{figure}
% \end{frame}

@@

            \vspace{2.5mm}
            \item Discuss how framework can reconcile conflicting findings on effect of federal Empowerment Zones \begin{citecolor}\citep{Busso_Gregory_Kline_2013,Neumark_Kolko_2010}\end{citecolor}

            \vspace{2.5mm}
            \item Event Study estimates of Community Health Centers find highly localized efffects \begin{citecolor}\citep{Bailey_Goodman_Bacon_2015}\end{citecolor}
        \end{itemize}
    \end{itemize} 
\end{frame}

@@

    \begin{itemize}
        \item $Y_{it}(D_i, \textcolor{alice}{h(\vec{D}, i)})$ is the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.

@@

        \pause
        \item The function $\textcolor{alice}{h(\vec{D}, i)}$ maps the entire treatment vector into an `exposure mapping' which can be a scalar or a vector.

        \pause
        \item No exposure is when $\textcolor{alice}{h(\vec{D}, i)} = \vec{0}$.
    \end{itemize}
\end{frame}

@@

        $\textcolor{alice}{h(\vec{D}, i)} = max_j \ 1\left(d(i, j\right) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.

@@

            \item Spillovers are non-additive, i.e. spillover effects do not depend on number of nearby treated areas
        \end{itemize}

@@

        $\textcolor{alice}{h(\vec{D}, i)} = max_j \ 1(d(i, j) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.

@@

        $\textcolor{alice}{h(\vec{D}, i)} = \sum_{j = 1}^k 1(d(i, j) \leq x)$.

        \begin{itemize}
            \item e.g. Amazon shipping center

@@

\begin{frame}{Estimand of Interest}
    \begin{block}{Estimand of Interest:}
    \[ 
        \textcolor{green}{\tau_{\text{direct}}} \equiv \textcolor{green}{\mathbb{E}\left[ Y_{i,1}(1, 0) - Y_{i,1}(0, 0) \mid D_i = 1\right]}
    \]
    \end{block}

    \pause
    \vspace{2.5mm}
    \begin{block}{Spillover Effects:}
    \[
        \textcolor{red}{\tau_{\text{spillover, treated}}} \equiv \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]}
    \]

    \[ 
        \textcolor{coral}{\tau_{\text{spillover, control}}} = \textcolor{coral}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]}
    \]
    \end{block}
\end{frame}

@@

    \vspace{2.5mm}
    \begin{block}{Assumption: {\it Parallel Counterfactual Trends}}
    \begin{align*}
        \mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{alice}{\vec{0}}) - Y_{i,0}(0, \textcolor{alice}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 1 \big] = \ \mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{alice}{\vec{0}}) - Y_{i,0}(0, \textcolor{alice}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 0 \big]
    \end{align*}
    \end{block}

@@

    Changes in outcomes do not depend on treatment status

@@

    \begin{align*}
        \mathbb{E}\left[\hat{\tau}\right] &= \underbrace{\mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Difference-in-Differences}} \\[3mm]
        \pause&= 
        \textcolor{green}{\mathbb{E} \left[ Y_{i1}(1, 0) - Y_{i1}(0, 0) \mid D_i = 1 \right]} \\
        &\quad + \quad 
        \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]} \\ 
        &\quad - \quad  
        \textcolor{coral}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\[3mm]
        &= \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{coral}{\tau_{\text{spillover, control}}}
    \end{align*}

@@

\begin{frame}{Removing Bias}

    \begin{block}{Assumption: {\it Spillovers are Local}}

@@

        (i) For all units $i$,
        \[ 
            \min_{j: D_j = 1} d(i,j) > \bar{d} \implies h(\vec{D}, i) = \vec{0}. 
        \]

        (ii) There are treated and control units such that $\min_{j: \ D_j = 1} d(i,j) > \bar{d}$.

    \end{block}
\end{frame}

\begin{frame}{Removing Bias}
    With assumption that spillovers are local, define $S_it$ to be an indicator equal to one in the post period for all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).

    Estimation of the following equation:
    \[ 
        y_{it} = \mu_t + \mu_i + \tau D_{it} + \tau_{\text{spill,treat}} S_{it} * D_{it} + \tau_{\text{spill,control}} S_{it} * (1-D_{it}) + \varepsilon_{it}
    \]

    \begin{itemize}
        \item $\hat{\tau}$ is consistent for $\tau_{\text{direct}}$

        \item $\hat{\tau}_{\text{spill}}$'s are not consistent for average spillover effects (hence the need for rings).
    \end{itemize}

@@

\begin{frame}{Aside -- Removing ``contaminated'' controls}
    A common solution to the problem of spillover is to re-estimate on a subsample with neighboring control units removed.

@@

% ------------------------------------------------------------------------------
\section{Estimation of Spillovers}
% ------------------------------------------------------------------------------

\begin{frame}{Robustness to Misspecification}
    Generate data using the following data-generating process with different exposure mappings:

@@

    \begin{itemize}
        \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly.

        \item Details in the paper, but $\mu_t$ is normally distributed on a linear time trend, $\mu_i$ are normally distributed
    \end{itemize}

@@

    \begin{itemize}
        \item \textit{Decay}: 
        \begin{itemize}
            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
        \end{itemize}

@@

    \begin{itemize}
        \item \textit{Rings}: 
        \begin{itemize}
            \item Set of concentric rings. For each ring, indicator for nearest treated unit being within that distance bin
        \end{itemize}

@@

        \begin{adjustbox}{width = \textwidth, center}
            \begin{threeparttable}
                \begin{tabular}{@{} l rrrrrr @{}}
                    % Head
                    \toprule
                    & \multicolumn{6}{c}{Data-Generating Process} \\
                    \cmidrule{2-7}

@@

    \onslide<3->{
        \textbf{Indicator (or set of rings) that captures \emph{all} affected unit removes all bias}
    }
\end{frame}

@@

    However, the two other spillover effects are of interest as well:
    \begin{itemize}
        \item $\textcolor{coral}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?

@@

\begin{frame}
    \begin{figure}[tb!]
        \caption{Single Ring - Removes spillover effects}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics{../../figures/figure-within_example.pdf}
            }
        \end{center}
    \end{figure}
\end{frame}

\begin{frame}
    \begin{figure}[tb!]
        \caption{Multiple Rings - Improves estimation of spillover effects}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics{../../figures/figure-rings_example.pdf}
                } 
            \end{center}
    \end{figure}
\end{frame}

@@

    \pause
    Research Questions:
    \begin{itemize}
        \item What are the local effects of TVA on manufacturing and agricultural economies?
        \item Do these effects come at the cost of other counties?
    \end{itemize}
\end{frame}

@@

    \begin{itemize}
        \item $\text{Ring}(d)$ is a set of indicators for being in the following distance bins (in miles) from the Tennessee Valley Authority: 
        \[ d \in \left\{ (0, 50], (50, 100], (100, 150] (150, 200]\right\} \]
    \end{itemize}
\end{frame}

@@

    \begin{adjustbox}{width = 1\textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} l c@{\extracolsep{20pt}}c@{\extracolsep{4pt}}cccc @{}}
                % Head
                \toprule

                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{5}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
                \cmidrule{2-2} \cmidrule{3-7}
                & & & TVA between & TVA between & TVA between & TVA between \\ 
                & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. & 150-200 mi. \\ 
                \textit{Dependent Var.} & (1) & (2) & (3) & (4) & (5) & (6) \\

@@

                Agricultural employment     & $-0.0514^{***}$ & $-0.0739^{***}$& $-0.0371^{***}$&    $-0.0164$   & $-0.0298^{***}$&  $-0.0157^{*}$ \\
                &   $(0.0114)$   &   $(0.0142)$   &   $(0.0002)$   &   $(0.0114)$   &   $(0.0096)$   &   $(0.0088)$

                \onslide<2->{
                    \\
                    Manufacturing employment    & $0.0560^{***}$ &    $0.0350$    & $-0.0203^{***}$&    $-0.0245$   &  $-0.0331^{*}$ & $-0.0296^{**}$ \\
                    &   $(0.0161)$   &   $(0.0218)$   &   $(0.0006)$   &   $(0.0282)$   &   $(0.0189)$   &   $(0.0142)$ 
                }

@@

    \begin{itemize}
        \item \citet{Busso_Gregory_Kline_2013} compare census tracts in Empowerment Zones to census tracts that qualified and were rejected from the program. They find significant large reduction of poverty.

@@

\section{Event Study}

\begin{frame}{Gardner (2021) Overview}

    \[ 
        y_{it} = \mu_i + \mu_t + \tau D_{it} + \varepsilon_{it}
    \]

    The problem with estimating this by OLS is that the treatment variable becomes residualized $\tilde{D}_{it}$ and this leads to all sorts of problems... (see new diff-in-diff literature)

    \pause

    Gardner (2021) recommends a two-step approach:

    1. Estimate $\mu_i$ and $\mu_t$ using never-treated/not-year-treated observations ($D_{it}$ = 0). Then subtract off $\hat{\mu}_i$ and $\hat{\mu}_t$.

    \pause
    2. Then, regress $y_{it} - \hat{\mu}_i - \hat{\mu}_t \equiv \tilde{y}_{it}$ on $\tau D_{it}$ (or event study leads/lags). This estimate is unbiased because $D_{it}$ is non-residualized (standard errors require adjusting).
\end{frame}

\begin{frame}{Controlling for Spillovers in Staggered Treatment Timing}
    \[ 
        y_{it} = \mu_i + \mu_t + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}} + \varepsilon_{it}
    \]

    Adjust two-step approach:

    \pause

    1. Estimate $\mu_i$ and $\mu_t$ using observations that aren't yet treated/affected by spillovers ($D_{it} = 0$ and $Within_{it} = 0$). Then subtract off $\hat{\mu}_i$ and $\hat{\mu}_t$.

    2. Then, regress $\tilde{y}_{it}$ on $\tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}}$ (or interacted event study leads/lags). This estimate is unbiased because $D_{it}$ is non-residualized (standard errors require adjusting).

\begin{frame}{Community Health Centers}
    \begin{citecolor}\citet{Bailey_Goodman_Bacon_2015}\end{citecolor} study the creation of federal community health centers between 1965 and 1974

    \textbf{Research Question:} Do low-/no-cost health services lower the mortality rate of the treated counties? \emph{New Question:} Do these effects spread to neighboring counties?
\end{frame}

\begin{frame}
    \begin{figure}[tb!]
        \caption{Effects of Establishment of Community Health Centers}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics[width=\textwidth]{../../figures/figure-chc-es_original.pdf}
            }
        \end{center}
    \end{figure}
\end{frame}

\begin{frame}
    \begin{figure}[tb!]
        \caption{Direct and Spillover Effects of Community Health Centers}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics[width=\textwidth]{../../figures/figure-chc-es_combined.pdf}
            }
        \end{center}
    \end{figure}
\end{frame}
